Verifying Demonstrations

### 2020-04-21 paper/protocol-trusted.tex
Edits trusted-witness counting section

\subsection{Count and Verification}%
\label{ProtocolVerification}

@@

To count or verify the participation count for a protest \(\prtst\) with 
identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
\begin{enumerate*}
\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
\item the participation proof \(\prf_{j}\) for each protester \(j\),
\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
  for all protesters in \(\prtst\), and finally,
\item the participation count, \ie the cardinality of 
  \(\prfs_\prtst^{\str,\theta}\).
\end{enumerate*}

More precisely, given \[
  \pshs_{\cid_0} = \{ (\cid, \pid, \wid, l, t_s, t_s', t_c, \corr) \in \pshs 
  \mid \cid = \cid_0 \}
\] and a matching pair \((s_P, s_W) \in {\pshs_{\cid_0}}^2\) for a witness 
\(i\) and a protester \(j\) with
\begin{align*}
  s_P &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c, \corr_i) &\text{and} \\
  s_W &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c', \corr_j),
\end{align*}
%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
the verifier can build a valid proof share \(s_j^{(i)}\) certified by \(i\) for 
\(j\) as follows:
verify \(\corr_i\) and \(\corr_j\),
let
\begin{align*}
  t &= \interval{\max(t_s, t_s')}{\min(t_c, t_c')} &\text{and} \\
  s_j^{(i)} &= (\cid_0, \pid_j, \wid_i, l, t),
\end{align*}
as in \cref{DefProofShare},
check that \(s_j^{(i)}\) is valid (\ie happened during and at the location of 
the protest), as in \cref{DefProofShare}.

Then the set of all valid proof shares for a protester \(j\) constitutes its 
participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by  \cref{DefParticipationCount}.

% MOST PROBABLY obsolete below v

%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
%(see \cref{DefProtest}), a verifier must download all the proof shares \[
%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
%\(l_i\subseteq  l\).
%Any proof share that does not verify correctly will be discarded.
%At this point, the verifier has constructed the set \(S\) from 
%\cref{DefProofShares} and can thus construct any participation proof 
%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
%    \theta}|\) as in \cref{DefParticipationCount}.

%__________________________

% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the verifier of which proof shares they
have signed, \eg by giving a list of all such proof shares or
digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a
  group or ring signature scheme for a set of potentially trusted witnesses, \eg
  members of an independent journalist association.  Then one learns
  that at least one member of this set must have
  been there.
}.

>>>>

\subsection{Count and verification}%
\label{ProtocolVerification}

@@

Assume that the verifier wants to verify the count for a protest~\(\prtst\).
The first thing the verifier will do, is to download all the proof 
shares~\(\psh\) from the ledger~\(\TS\), such that \(\psh \sqsubseteq \sprtst\) 
is a valid proof share for some subprotest~\(\sprtst\in\prtst\) of the 
protest~\(\prtst\).
Next, the verifier selects only those proof shares~\(\psh = (\cid, \pid, \wid, 
t, l, \corr_{\wid})\) such that \(\corr_\wid\) proves knowledge of a signature 
by \(\sskw\), where \(\CA'\) is someone the verifier trusts\footnote{%
  We note that there can be more than one \ac{CA} which the verifier trusts 
  will issue credential only to trustworthy witnesses,
  but we keep to one for the simplicity of our exposition.
}.
We denote this set of proof shares by \(\pshs\).

Next, the verifier partitions the set of proof shares~\(\pshs\) using the 
relation~\(=_\pid\) such that \(
  (\cid, \pid, \wid, t, l) =_\pid (\cid', \pid', \wid', t', l')
\) is true if \(\pid = \pid'\).
Each equivalence class \(\prf_{i, \prtst} \in \pshs/=_\pid\) is a proof of 
participation for participant \(i\).
In terms of \cref{DefParticipationCount}, the set of 
proofs~\(\prfs_\prtst^{\str, \theta} = \pshs/=_\pid\), where \(\theta = 1\) and 
\(\str(\cdot) = 1\).
Consequently, the total participation count is \(|\pshs/=_\pid|\).

\endinput
